### 2017-02-04 manuscript.rmd
Update manuscript.rmd
Fixes a couple of typos

We reanalyzed the the KMRR study using phylogenetic comparative methods, focusing on the dataset of Brawand *et al.* 2011 [@Brawand:2011du]. For each internal node in each gene tree (Figure 1b), we measured the phylogenetic independent contrast (PIC) [@Felsenstein:1985ua] of the expression statistic Tau. This is the difference in values of Tau for descendant nodes scaled by the expected variance (determined largely by the lengths of these branches). These contrasts were then annotated by whether they are made across a speciation or duplication event. The original description of independent contrasts [@Felsenstein:1985ua] focused on assessing covariance between changes in two traits on a tree. Our use of contrasts is a bit different-- we look for differences in evolutionary changes of one trait (differential expression) between two categories of nodes (speciation and duplication) on a tree.

@@

The independent contrast across a node is the amount of change observed between the daughter notes, scaled by the expected variance [@Felsenstein:1985ua]. The expected variance is principally determined by the lengths of the branches leading from the node to these daughters. The shorter the total length of the two branches leading to daughter nodes, the larger the contrast for a given observed difference. This is because the same difference across a shorter total branch length indicates a greater rate of evolutionary change. The expected variance of contrasts for speciation nodes is constrained by the branch lengths on the species tree, but the expected variance of contrasts for duplications has a much wider range (Figure XXAscertainment c). This could lead to biases if the lengths of branches that descend from duplication nodes tend to be overestimated. We therefore examined only the contrasts that fell within in the range of expected variance seen for speciation contrasts, excluding duplication contrasts that fall outside of this range. This reanalysis does not reject the ortholog conjecture either (Figure XXAscertainment d), indicating that branch length bias is not responsible for the result.

>>>>

We reanalyzed the KMRR study using phylogenetic comparative methods, focusing on the dataset of Brawand *et al.* 2011 [@Brawand:2011du]. For each internal node in each gene tree (Figure 1b), we measured the phylogenetic independent contrast (PIC) [@Felsenstein:1985ua] of the expression statistic Tau. This is the difference in values of Tau for descendant nodes scaled by the expected variance (determined largely by the lengths of these branches). These contrasts were then annotated by whether they are made across a speciation or duplication event. The original description of independent contrasts [@Felsenstein:1985ua] focused on assessing covariance between changes in two traits on a tree. Our use of contrasts is a bit different-- we look for differences in evolutionary changes of one trait (differential expression) between two categories of nodes (speciation and duplication) on a tree.

@@

The independent contrast across a node is the amount of change observed between the daughter notes, scaled by the expected variance [@Felsenstein:1985ua]. The expected variance is principally determined by the lengths of the branches leading from the node to these daughters. The shorter the total length of the two branches leading to daughter nodes, the larger the contrast for a given observed difference. This is because the same difference across a shorter total branch length indicates a greater rate of evolutionary change. The expected variance of contrasts for speciation nodes is constrained by the branch lengths on the species tree, but the expected variance of contrasts for duplications has a much wider range (Figure XXAscertainment c). This could lead to biases if the lengths of branches that descend from duplication nodes tend to be overestimated. We therefore examined only the contrasts that fell within in the range of expected variance seen for speciation contrasts, excluding duplication contrasts that fall outside of this range. This reanalysis does not reject the null hypothesis either (Figure XXAscertainment d), indicating that branch length bias is not responsible for the result.
